---
title: "Supplementary information: Evaluating the impact of modelling strain dynamics on short-term COVID-19 forecast performance"
output: 
  html_document:
    keep_md: true
    toc: true
    theme: united
vignette: >
  %\VignetteIndexEntry{Evaluating the impact of modelling strain dynamics on short-term COVID-19 forecast performance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: library.bib
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/apa-numeric-superscript-brackets.csl
header-includes:
   - \usepackage{float}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, eval = TRUE,
  fig.width = 9, fig.height = 9,
  dpi = 320,
  fig.path = "figures/"
)
```


```{r, message = FALSE}
library(forecast.vocs)
```

*Note: Sub-headings where non-standard are there to guide the writing process and will be removed in the final draft.*

## Authors

S. Abbott (1), J. Bracher (2), S. Funk (1), ... (TBD)

Correspondence to: sam.abbott@lshtm.ac.uk

## Affiliations

1. Center for the Mathematical Modelling of Infectious Diseases, London School of Hygiene & Tropical Medicine, London WC1E 7HT, United Kingdom
2. Chair of Statistics and Econometrics, Karlsruhe Institute of Technology (KIT), Karlsruhe, Germany


## References

<div id = 'refs'></div>
